\documentclass[margin,line,11pt]{res}
\usepackage{fontspec} 
\usepackage{enumitem}
\setmainfont{Linux Libertine O}
\usepackage{multicol}                      
\usepackage{marvosym} % For cool symbols. 
\usepackage{color,hyperref}
\definecolor{blue}{rgb}{0,0,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=blue,linkcolor=blue}

%% \oddsidemargin -.5in
%% \evensidemargin -.5in
\textwidth=5.8in
%\itemsep=0in

\begin{document}

\name{\Huge{Shiwali Mohan} \vspace*{.05in}}

\thispagestyle{empty}
\begin{resume}
  \section{\sc Contact Information}
  \vspace{.05in}
  \begin{tabular}{@{}p{3in}p{4in}}            
    382 Ventura Avenue,                  & {\it cell:}    (734) 757-0354 \\         
    Palo Alto,                            & {\it email:}  shiwali.mohan@gmail.com\\       
    California 94306                          & {\it url:} www.shiwali.me \\     
  \end{tabular}


%%  \section{\sc Research \\Interests}
%%  Interactive AI/machine learning agents, cognitive systems and modeling, situated language processing 

  \section{\sc Education}
          {\bf University of Michigan}, Ann Arbor, MI USA\\
          Ph.D., Computer Science and Engineering \hfill 2015 

          {\bf University of Michigan}, Ann Arbor, MI USA\\
          M.S.E., Computer Science and Engineering \hfill 2009

          {\bf University of Delhi}, New Delhi, India\\
          {\em Netaji Subhas Institute of Technology}\\
          B.E.,  Instrumentation and Control Engineering \hfill 2007
  
\section{\sc Employment}
          {\bf Palo Alto Research Center}, Palo Alto, CA USA \\
          {Member of Research Staff}  \hfill January 2016 - \emph{present}
                  
          {\bf Palo Alto Research Center}, Palo Alto, CA USA \\
          {Postdoctoral Researcher} \hfill November 2014 - December 2015 
                  
          {\bf Yahoo! Research and Development}, Bangalore, Karnataka India \\
          {Software Development Engineering} \hfill August 2007 - July 2008


          \section{\sc Awards and Honors}
          Blue Sky Award \hfill AAAI 2018\\
          Best Paper Award \hfill CICLING 2008\\
          
          

          \section{\sc Funding}
          Air Force Office of Scientific Research (AFOSR) \hfill February 2018 - July 2019\\
          Levels of Learning in Natural and Artificial Agents\\
          Co-Principal Investigator, $\$164,362.47$\\
       
          Advanced Research Projects Agency-Energy (ARPA-E) \hfill January 2017 - July 2018 \\
          Collaborative Optimization and Planning for Transportation Energy Reduction\\
          Key contributor, $\$2,177,717.00$\\
          


\section{\sc Publications}
\textbf{Dissertation}
\begin{enumerate}[label=\lbrack D\arabic*\rbrack, leftmargin=*]
\item \textbf{Shiwali Mohan}.  From Verbs to Tasks: An Integrated Account of Task Learning from Situated Interactive Instruction. \emph{University of Michigan, Ann Arbor}, 2015.
\end{enumerate}

\textbf{Book Chapters}
\begin{enumerate}[label=\lbrack B\arabic*\rbrack, leftmargin=*]
\item John Laird, \textbf{Shiwali Mohan}, James Kirk, Aaron Mininger. The Learning Problem in Interactive Task Learning. \emph{Ernst Strunngman Forum - Interactive Task Learning  Agents, Robots, and Humans and Acquiring New Tasks through Natural Interaction (invited, to appear)}. 2017.
  \item Dario Salvucci, John Laird, Fredrick Chang, Kenneth Forbus, Parisa Kordjamshidi, Tom Mitchell, \textbf{Shiwali Mohan}, Michael Spranger, S Stevenson, Andrea Stocco, Gregory Trafton. Learning in Interactive Task Learning. \emph{Ernst Strunngman Forum - Interactive Task Learning  Agents, Robots, and Humans and Acquiring New Tasks through Natural Interaction (to appear)} 2017. 
  \end{enumerate}

\textbf{Journal Articles}
\begin{enumerate}[label=\lbrack J\arabic*\rbrack, leftmargin=*]
\item \textbf{Shiwali Mohan}, Anusha Venkatakrishnan, Andrea Hartzler. Observations from Deploying an Intelligent Interactive Health Coach to Promote Aerobic Exercise. \emph{Under review}. 2018.
    \item \textbf{Shiwali Mohan}, Anusha Venkatakrishnan, Peter Pirolli, Les Nelson, Michael Silva. On Developing Behavior Change Theory-based Coaching Interactions for a Comprehensive mHealth System. \emph{In preparation}. 2018.
\item Aaron Springer, Anusha Venkatakrishnan, \textbf{Shiwali Mohan}, Les Nelson, Michael Silva, Peter Pirolli. Leveraging Self-Affirmation to Increase mHealth Behavior Change. \emph{Journal of Medical Information Research}. 2018.
\item Peter Pirolli, \textbf{Shiwali Mohan}, Anusha Venkatakrishnan, Len Nelson, Michael Silva, Aaron Springer. \emph{Journal of Medical Information Research}. 2017.
\item John E Laird, Kevin Gluck, John Anderson, Kenneth D Forbus, Odest Chadwicke Jenkins, Christian Lebiere, Dario Salvucci, Matthias Scheutz, Andrea Thomaz, Greg Trafton, Robert E Wray, \textbf{Shiwali Mohan}, James R Kirk. Interactive Task Learning. \emph{IEEE Intelligent Systems}, Volume 32, Issue 4, IEEE 2017.
\item \textbf{Shiwali Mohan}, Aaron Mininger, and John Laird. Towards an Indexical model of Situated Comprehension for Real-World Cognitive Agents. \emph{Advances in Cognitive Systems 3}, ACS 2014.
\item John Laird and \textbf{Shiwali Mohan}. A Case Study of Knowledge Integration Across Multiple Memories in Soar. \emph{Biologically Inspired Cognitive Architectures} (invited), BICA 2014.
\item \textbf{Shiwali Mohan}, Aaron Mininger, James Kirk, and John Laird. Acquiring Grounded Representations of Words with Situated Interactive Instruction. \emph{Advances in Cognitive Systems 2}, ACS 2012.
\end{enumerate}


\textbf{Conference Proceedings}
\begin{enumerate}[label=\lbrack C\arabic*\rbrack,leftmargin=*]
  \item \textbf{Shiwali Mohan}, Frances Yan, Victoria Bellotti, Hesham Rakha, Matthew Klenk, On Influencing Individual Behavior for Reducing Transportation Energy Expenditure in a Large Population. \emph{Under review}. 2019
  \item John Laird and \textbf{Shiwali Mohan}. Learning Fast and Slow: Levels of Learning in General Autonomous Intelligent Agents. \emph{(to appear) In the Proceedings of the $32^{nd}$ AAAI Conference}. AAAI 2018. Blue Sky Award.
  \item \textbf{Shiwali Mohan}, Anusha Venkatakrishnan, Michael Silva, and Peter Pirolli. On Designing a Social Coach to Promote Regular Aerobic Exercise. \emph{In the Proceedings of the 29th Annual Conference on Innovative Applications of Artificial Intelligence/AAAI}, IAAI 2017.
  \item Justin Li, Steven Jones, \textbf{Shiwali Mohan}, and Nate Derbinksy. Architectural Mechanisms for Mitigating Uncertainty during Long-Term Declarative Knowledge Access. \emph{In the Proceedings of the 4th Conference on Advances in Cognitive Systems}, ACS 2016.
  \item Andrea L Hartzler, Anusha Venkatakrishnan, \textbf{Shiwali Mohan}, Michael Silva, Paula Lozano, James D Ralston, Evette Ludman, Dori Rosenberg, Katherine M Newton, Lester Nelson, Peter Pirolli. Acceptability of a Team-Based Mobile Health (mHealth) Application for Lifestlye Self-Management in Individuals with Chronic Illnesses. \emph{In $38^{th}$ Annual International Conference of the Engineering in Medicine and Biology Society (EMBC)}, IEEE. 2016.
  \item \textbf{Shiwali Mohan} and John Laird. Learning Goal-Oriented Hierarchical Tasks from Situated Interactive Instruction. \emph{In the Proceedings of the 28th AAAI Conference}, AAAI 2014.
  \item \textbf{Shiwali Mohan}, James Kirk, and John Laird. A Computational Model of Situated Task Learning with Interactive Instruction. \emph{In Proceedings of the 17th International Conference on Computational Modeling}, ICCM 2013.
  \item Mandar Joshi, Rakesh Khobragade, Saurabh Sarda, Umesh Deshpande, and \textbf{Shiwali Mohan}. Object-Oriented Representation and Hierarchical Reinforcement Learning in Infinite Mario. \emph{In Proceedings of the 24th IEEE International Conference on Tools with Artificial Intelligence}, ICTAI 2012.
  \item \textbf{Shiwali Mohan} and John Laird. An Object-Oriented Approach to Reinforcement Learning in an Action Game. \emph{In Proceedings of the 7th Artificial Intelligence for Interactive Digital Entertainment Conference}, AIIDE 2011.
  \item Niladri Chatterjee and \textbf{Shiwali Mohan}. Discovering Word Senses from Text using Random Indexing. \emph{In Proceedings of the 9th International Conference on Computational linguistics and Intelligent Text Processing}, CICLing 2008. Best Paper Award.
  \item Niladri Chatterjee and \textbf{Shiwali Mohan}. Extraction-based Single-Document Summarization Using Random Indexing. \emph{In Proceeding of the 19th IEEE International Conference on Tools with Artificial Intelligence}, ICTAI 2007.
\end{enumerate}

\textbf{Refereed Symposia/Workshop Proceedings}
\begin{enumerate}[label=\lbrack W\arabic*\rbrack:,leftmargin=*]
\item \textbf{Shiwali Mohan}, Kalai Ramea, Bob Price, Matthew Shreve, Hoda Eldardiry. Building \textsc{JARVIS}: Towards Real-time Contextual Planning for Live Instructional Support in Physical Tasks.\emph{Under review}. 2019.
\item Filip Dvorak, \textbf{Shiwali Mohan}, Victoria Bellotti, Matthew Klenk. Collaborative Optimization and Planning for Transportation Energy Reduction. \emph{ICAPS Proceedings of the 6th Workshop on Distributed and Multi-Agent Planning}. 2018.
\item \textbf{Shiwali Mohan}, Anusha Venkatakrishnan, Daniel Bobrow, Peter Pirolli. Health Behavior Change: A Motivating Domain for Human-Aware AI Research. \emph{In Proceeding of the AAAI 2017 Workshops}. AAAI 2017.
  
\item Matthew Klenk, \textbf{Shiwali Mohan}, Johan de Kleer, Daniel Bobrow, Tom Hinrichs, Ken Forbus. Collaborative Autonomy Through Analogical Comic Graphs. \emph{In Proceedings of AAAI 2017 Workshops}. AAAI 2017.
  
\item John E. Laird and \textbf{Shiwali Mohan}. A Case Study of Knowledge Integration Across Multiple Memories in Soar. \emph{In Papers from the AAAI Fall Symposium Series on Integrated Cognition}, 2013.
  
\item \textbf{Shiwali Mohan}*, Aaron Mininger*, James Kirk*, and John Laird. Learning Grounded Language Through Situated Interactive Instruction. \emph{In Papers from the AAAI Fall Symposium Series on Robots Learning Interactively from Human Teachers}, 2012.

\item John Laird, Keegan Kinkade, \textbf{Shiwali Mohan}, and Joseph Xu. Cognitive Robotics Using the Soar Cognitive Architecture. \emph{In Proceedings of the 8th International Cognitive Robotics Workshop}, 2012.

\item \textbf{Shiwali Mohan} and John Laird. Situated Comprehension of Imperative Sentences in Embodied, Cognitive Agents. \emph{In Papers from the AAAI Workshop on Grounding Language for Physical Systems}, 2012.
  
\item \textbf{Shiwali Mohan} and John Laird. Towards Situated, Interactive, Instructable Agents in a Cognitive Architecture. \emph{In Papers from the AAAI Fall Symposium Series on Advances in Cognitive Systems}, 2011.
\end{enumerate}

\textbf{Refereed Extended Abstracts}
\begin{enumerate}[label=\lbrack A\arabic*\rbrack,leftmargin=*]
\item Peter Pirolli, \textbf{Shiwali Mohan}, Rong Yang, Anusha Venkatakrishnan, Michael Silva, Michael Youngblood, Ashwin Ram and Les Nelson. User Modeling and Planning for Improving Self-efficacy and Goal Adherence in mHealth. \emph{Frontiers Public Health. Conference Abstract: 2nd Behaviour Change Conference: Digital Health and Wellbeing.}, 2016.
\item \textbf{Shiwali Mohan}, and John E. Laird. Learning New Tasks for Situated Interactive Instruction. \emph{In the 2014 HRI Pioneers Workshop at Human-Robot Interaction}, 2014.
\item Mandar Joshi, Rakesh Khobragade, Saurabh Sarda, Umesh Deshpande, and \textbf{Shiwali Mohan}. Hierarchical Action selection for Reinforcement Learning in Infinite Mario. \emph{In Proceedings of the 6th Starting Artificial Intelligence Research Symposium at European Conference on Artificial Intelligence}, STAIRS 2012.

\item \textbf{Shiwali Mohan} and John Laird. Learning Actions and Action Verbs from Human-Agent Interaction. \emph{In Proceedings of the 26th AAAI Conference on Artificial Intelligence}, AAAI 2012.

\item \textbf{Shiwali Mohan} and John Laird. Exploring Mixed-Initiative Interaction for Learning with Situated Instruction in Cognitive Agents. \emph{In Proceedings of the 26th AAAI Conference on Artificial Intelligence}, AAAI 2012.

\item \textbf{Shiwali Mohan} and John Laird. Relational Reinforcement Learning in Infinite Mario. \emph{In Proceedings of the 24th AAAI Conference on Artificial Intelligence}, AAAI 2010.
\end{enumerate}


\section{\sc Patents}
Ashwin Ram, Gregory Michael Youngblood, Lester D Nelson, Anusha Venkatakrishnan, Peter L Pirolli, Michael K Silva, Shiwali Mohan. \emph{System and Method to Create, Monitor, and Adapt Individualized Multidimensional Health Programs}. Application number: 15/130,770. Publication date: 2016/4/15.







\section{\sc Invited Talks, Workshops, \& Panels}
NSF Workshop on Interactive Cognitive Assistants \hfill November 2017\\
Ernst Strunngmann Forum on Interactive Task Learning \hfill May 2017\\ \\
\emph{On Designing a Programmable Cognitive Assistant}\\ IBM Cognitive Systems Institute \hfill September 2015\\ \\
\emph{Learning Hierarchical Tasks with Situated Interactive Instruction}\\ Information Sciences Institute, Los Angeles \hfill December 2013\\
Interaction Lab, Computer Science and Engineering, USC \hfill December 2013\\
University of California, Los Angeles \hfill November 2013\\
USC Institute for Creative Technologies \hfill November 2013

\section{\sc Honors and Awards}
Blue Sky Award, AAAI \hfill 2018\\
HRI Pioneers Scholarship \hfill 2014\\
AAAI Travel Grant, AAAI Fall Symposium Series \hfill 2013\\
Doctoral Consortium Scholarship, AAAI \hfill 2012 \\
Rackham Travel Grant \hfill 2011, 2012, 2013 \\
Best Paper Award, CICLing \hfill 2008 \\
Scholarship for Academic Excellence at the University of Delhi \hfill 2003 - 2007

\section{\sc Media}
\emph{Could a Bot Coach You to a New PR? Artificial intelligence is making its way into fitness apps}. Interview. Outside magazine. \hfill 2017


\section{\sc Service}
\emph{Program Committee}: ICRA, HRI, IUI, AAAI, AAAI Doctoral Consortium \hfill 2018\\
\emph{Reviewer}: Autonomous  Robots \hfill 2018\\
\emph{Program Committee}: AAAI, AAAI Doctoral Consortium \hfill 2017\\
\emph{Program Committee} IJCAI, AAAI \hfill 2016\\
\emph{Program Committee} AI-HRI AAAI Fall Symposium Series \hfill 2015\\
\emph{Organizing Committee}, Students of Cognitive Systems at ACS \hfill 2015\\






%% \section{\sc Skills}
%% Programming: Java, Python \\
%% AI Architecture: Soar \\
%% Machine Learning: Scikit-learn, H2O\\
%% Data Analysis: R, Pandas, Numpy \\



               %   \section{\sc Teaching Experience}
               %   \textbf{University of Michigan}, Ann Arbor, MI, USA
               %   \\ \emph{Guest Lecturer}: Cognition and Interactive
               %   Systems \hfill April 2014 \\ EECS 498: Intelligent
               %   Interactive Systems

                %  \textbf{University of Michigan}, Ann Arbor, MI, USA \\
                %  \emph{Graduate Student Instructor} \hfill January 2012 - April 2012 \\
                %  EECS 492: Introduction to Artificial Intelligence/AAAI

                %  \section{\sc Advising Experience}
                %  \textbf{Bharati Vidyapeeth College of Engineering}, New Delhi, India\\
                %  Senior thesis: \emph{Designing Soar agents for planet wars} \hfill September 2012 - Present\\
                %  Students: Anant Mittal, Anmol Gupta

                %  \textbf{Visvesvaraya National Institute of
                %    Technology}, Nagpur, India\\ Senior thesis:
                %  \emph{Reinforcement learning agents for Infinite
                %    Mario} \hfill September 2011 - May
                %  2012\\ Students: Mandar Joshi, Rakesh Khobragade,
                %  Saurabh Sarda\\





\end{resume}
\end{document}



