\documentclass[margin,line,11pt]{res}
\usepackage{fontspec} 
\usepackage{enumitem}
\setmainfont{Linux Libertine O}
\usepackage{multicol}                      
\usepackage{marvosym} % For cool symbols. 
\usepackage{color,hyperref}
\definecolor{blue}{rgb}{0,0,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=blue,linkcolor=blue}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.2in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\begin{document}

\name{\Huge{Shiwali Mohan} \vspace*{.1in}}

\thispagestyle{empty}
\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Bob \& Betty Beyster Building, \#3844             & {\it work:}  (734) 763-0120 \\            
Computer Science and Engineering                  & {\it cell:}    (734) 757-0354 \\         
University of Michigan                            & {\it email:}  shiwali@umich.edu\\       
Ann Arbor, MI  48109 USA                          & {\it url:} www.shiwali.me \\     
\end{tabular}


\section{\sc Research \\Interests}
Cognitive systems and agents, situated language for agents, learning with human-agent interaction, natural language semantics, knowledge representation and reasoning, interactive knowledge acquisition, cognitive robotics.

\section{\sc Education}
{\bf University of Michigan}, Ann Arbor, MI USA\\
Ph.D., Computer Science and Engineering \hfill 2008 - 2014 (expected)\\
Thesis (in progress):  \emph{Learning Tasks and Verbs from Situated Interactive Instruction} \\
Thesis Advisor:  John Laird \\
Thesis Committee: Edmund Durfee, Richard Lewis, Edwin Olson, Andrea Thomaz

{\bf University of Michigan}, Ann Arbor, MI USA\\
M.S.E., Computer Science and Engineering \hfill 2008 - 2009

{\bf University of Delhi}, New Delhi, India\\
{\em Netaji Subhas Institute of Technology}\\
B.E.,  Instrumentation and Control Engineering \hfill 2003 - 2007\\ 
Senior Thesis: \emph{Extraction-based Single Document Summarization}



\section{\sc Research Experience}
{\bf University of Michigan}, Ann Arbor, MI USA \\ {Graduate Student
  Research Assistant} to John E. Laird \hfill August 2010 -
present\\ \emph{Learning tasks with situated interactive instruction}
\\ Studying representations and knowledge-intensive learning algorithms
that are useful in learning goal-oriented, hierarchical tasks from
mixed-initiative task-oriented dialog. Developing paradigms to learn with task-oriented dialog.

\emph{Situated language for embodied agents}\\ 
Developing the Indexical model of situated comprehension that
translates abstract linguistic symbols to grounded perceptual, spatial, and
task knowledge. Investigating the role of non-linguistic context and
domain knowledge in linguistic comprehension. 

{\bf University of Michigan}, Ann Arbor, MI USA \\
{Graduate Student Research Assistant} to John E. Laird \hfill January 2009 - August 2010\\
\emph{Reinforcement learning in Soar cognitive architecture}\\
 Designed, implemented, and analyzed reinforcement learning agents for
 Infinite Mario. Formulated and implemented modular reinforcement learning for the Soar cognitive
 architecture to simultaneously learning multiple markov decision processes. 

{\bf Indian Institute of Technology}, New Delhi, India \\
{Research Assistant} to Niladri Chatterjee \hfill May 2007 - July 2007\\
\emph{Sense disambiguation, distributional semantics}\\
Developed and analyzed a Random Indexing based algorithm for sense disambiguation of homonyms.

{\bf University of Delhi}, New Delhi, India \\
{Thesis} with Shampa Chakravarty, Niladri Chatterjee \hfill December 2006 - May 2007\\
\emph{Single document summarization, distributional semantics}\\
Developed and analyzed an algorithm for single-document summarization using PageRank and Random Indexing.


\section{\sc Publications}
\textbf{Journal Articles}
\begin{enumerate}[label=\lbrack J\arabic*\rbrack, leftmargin=*]
\item \textbf{Shiwali Mohan}, Aaron Mininger, and John Laird. Towards an indexical model of situated comprehension for real-world cognitive agents. \emph{Advances in Cognitive Systems 3} (in print), ACS 2013.
\item John Laird and \textbf{Shiwali Mohan}. A case study of knowledge integration across multiple memories in Soar. \emph{Biologically Inspired Cognitive Architectures} (invited, in submission), BICA 2014.
\item \textbf{Shiwali Mohan}, Aaron Mininger, James Kirk, and John Laird. Acquiring grounded representations of words with situated interactive instruction. \emph{Advances in Cognitive Systems 2}, ACS 2012.
\end{enumerate}

\textbf{Conference Proceedings}
\begin{enumerate}[label=\lbrack C\arabic*\rbrack,leftmargin=*]
\item \textbf{Shiwali Mohan}, Aaron Mininger, and John Laird. Towards an indexical model of situated comprehension for real-world cognitive agents. \emph{In Proceedings of the 2nd Conference on Advances in Cognitive Systems}, ACS 2013.
\item \textbf{Shiwali Mohan}, James Kirk, and John Laird. A computational model of situated task learning with interactive instruction. \emph{In Proceedings of the 17th International Conference on Computational Modeling}, ICCM 2013.
\item Mandar Joshi, Rakesh Khobragade, Saurabh Sarda, Umesh Deshpande, and \textbf{Shiwali Mohan}. Object-oriented
representation and hierarchical reinforcement learning in Infinite Mario. \emph{In Proceedings of the 24th IEEE
International Conference on Tools with Artificial Intelligence}, ICTAI 2012.
\item \textbf{Shiwali Mohan} and John Laird. An Object-Oriented approach to reinforcement learning in an action game.
\emph{In Proceedings of the 7th Artificial Intelligence for Interactive Digital Entertainment Conference}, AIIDE 2011.
\item Niladri Chatterjee and \textbf{Shiwali Mohan}. Discovering word senses from text using random indexing. \emph{In
Proceedings of the 9th International Conference on Computational linguistics and Intelligent Text Processing},
CICLing 2008. Best Paper Award.
\item Niladri Chaerjee and \textbf{Shiwali Mohan}. Extraction-based single-document summarization using random
indexing. \emph{In Proceeding of the 19th IEEE International Conference on Tools with Artificial Intelligence}, ICTAI
2007.
\end{enumerate}

\textbf{Refereed Symposia/Workshop Proceedings}
\begin{enumerate}[label=\lbrack W\arabic*\rbrack:,leftmargin=*]
\item John E. Laird and \textbf{Shiwali Mohan}. A case study of knowledge integration across multiple memories in
Soar. \emph{In Papers from the AAAI Fall Symposium Series on Integrated Cognition}, 2013.
\item \textbf{Shiwali Mohan}*, Aaron Mininger*, James Kirk*, and John Laird. Learning grounded language through
situated interactive instruction. \emph{In Papers from the AAAI Fall Symposium Series on Robots Learning Interactively from Human Teachers}, 2012.
\item John Laird, Keegan Kinkade, \textbf{Shiwali Mohan}, and Joseph Xu. Cognitive robotics using the soar cognitive
architecture. \emph{In Proceedings of the 8th International Cognitive Robotics Workshop}, 2012.
\item \textbf{Shiwali Mohan} and John Laird. Situated comprehension of imperative sentences in embodied, cognitive
agents. \emph{In Papers from the AAAI Workshop on Grounding Language for Physical Systems}, 2012.
\item \textbf{Shiwali Mohan} and John Laird. Towards situated, interactive, instructable agents in a cognitive architecture. \emph{In Papers from the AAAI Fall Symposium Series on Advances in Cognitive Systems}, 2011.
\end{enumerate}


\textbf{Refereed Extended Abstracts}
\begin{enumerate}[label=\lbrack A\arabic*\rbrack,leftmargin=*]
\item \textbf{Shiwali Mohan}, and John E. Laird. Learning new tasks for situated interactive instruction. \emph{In the 2014 HRI Pioneers Workshop at Human-Robot Interaction}, 2014.

\item Mandar Joshi, Rakesh Khobragade, Saurabh Sarda, Umesh Deshpande, and \textbf{Shiwali Mohan}. Hierarchical
action selection for reinforcement learning in Infinite Mario. \emph{In Proceedings of the 6th Starting Artificial
Intelligence Research Symposium at European Conference on Artificial Intelligence}, STAIRS 2012.

\item \textbf{Shiwali Mohan} and John Laird. Learning actions and action verbs from human-agent interaction. \emph{In
Proceedings of the 26th AAAI Conference on Artificial Intelligence}, AAAI 2012.

\item \textbf{Shiwali Mohan} and John Laird. Exploring mixed-initiative interaction for learning with situated instruction in cognitive agents. \emph{In Proceedings of the 26th AAAI Conference on Artificial Intelligence}, AAAI 2012.

\item \textbf{Shiwali Mohan} and John Laird. Relational reinforcement learning in Infinite Mario. \emph{In Proceedings of the
24th AAAI Conference on Artificial Intelligence}, AAAI 2010.
\end{enumerate}

\section{\sc Teaching Experience}
\textbf{University of Michigan}, Ann Arbor, MI, USA \\
\emph{Graduate Student Instructor} \hfill January 2012 - April 2012 \\
EECS 492: Introduction to Artificial Intelligence

\textbf{University of Michigan}, Ann Arbor, MI, USA \\
\emph{Student}  \hfill September 2011 - December 2011\\
EECS 580: Teaching Engineering

\section{\sc Advising Experience}
\textbf{Bharati Vidyapeeth College of Engineering}, New Delhi, India\\
Senior thesis: \emph{Designing Soar agents for planet wars} \hfill September 2012 - Present\\
Students: Anant Mittal, Anmol Gupta

\textbf{Visvesvaraya National Institute of Technology}, Nagpur, India\\
Senior thesis: \emph{Reinforcement learning agents for Infinite Mario} \hfill September 2011 - May 2012\\
Students: Mandar Joshi, Rakesh Khobragade, Saurabh Sarda\\

\section{\sc Talks}
\textbf{Learning Hierarchical Tasks with Situated Interactive Instruction}\\
Center for Vision, Cognition, Learning, and Art, UCLA \hfill November 2013\\
USC Institute for Creative Technologies. \hfill November 2013\\
Interaction Lab, Computer Science and Engineering, USC \hfill December 2013\\
Information Sciences Institute, Los Angeles \hfill December 2013

\section{\sc Service}
\emph{Co-Chair}, Special Interest Group - Faculty, University of Michigan \hfill 2013 \\
\emph{Co-Chair}, Special Interest Group - Faculty, University of Michigan \hfill 2012 \\
\emph{Vice-President}, CSE Graduate Organization, University of Michigan \hfill 2011 \\
\emph{Social Chair}, Indian Students Association, University of Michigan \hfill 2011\\
\emph{DCO Representative}, CSE Graduate Organization, University of Michigan \hfill 2010 \\
\emph{Social Chair}, Indian Students Association, University of Michigan \hfill 2010

\section{\sc Honors and Awards} 
HRI Pioneers Scholarship, 2014\\
AAAI Travel Grant, AAAI Fall Symposium Series: 2013\\
Doctoral Consortium Scholarship, AAAI: 2012 \\
Rackham Travel Grant: 2011, 2012, 2013 \\
Best Paper Award, CICLing: 2008 \\
Scholarship for Academic Excellence at the University of Delhi: 2003 - 2007 

\section{Skills}
Experience in intelligent agent design and cognitive architectures - Soar, ACT-R \\
Experience in Java, C/C++, Perl, Python

\section{\sc Industry Experience}
{\bf Yahoo! Research and Development}, Bangalore, India \\
\emph{Software Engineer} with Strategic Data Services \hfill July 2007 - July 2008\\
{\bf Bharat Electronics Limited}, Ghaziabad, India \\
\emph{Software Intern} \hfill May 2006 - July 2006\\
{\bf Central Research Laboratory}, Ghaziabad, India \\
\emph{Software Intern} \hfill May 2005 - July 2006 

\section{\sc References}
\vspace{-0.02cm}
\begin{multicols}{2}
\begin{itemize}
\item \textbf{John E. Laird} \\
  \emph{John L. Tishman Professor of Engineering} \\
  Computer Science and Engineering \\ 
  University of Michigan\\
  2260 Hayward Street\\
  Ann Arbor, MI 48109\\
  \href{mailto:laird@umich.edu}{laird@umich.edu}
\item \textbf{Edwin Olson} \\
  \emph{Assistant Professor} \\
  Computer Science and Engineering \\ 
  University of Michigan\\
  2260 Hayward Street\\
  Ann Arbor, MI 48109\\
  \href{mailto:ebolson@umich.edu}{ebolson@umich.edu}
\item \textbf{Richard Lewis} \\
  \emph{Professor of Psychology and Linguistics} \\
  Department of Psychology \\ 
  University of Michigan\\
  530 Church Street\\
  Ann Arbor, MI 48109\\
  \href{mailto:rickl@umich.edu}{rickl@umich.edu} \\
\item \textbf{Matthias Scheutz} \\
  \emph{Bernard M. Gordon Senior Faculty Fellow} \\
  Department of Computer Science\\
  Tufts University\\
  200 Boston Avenue\\
  Medford, MA 02155\\
  \href{mailto:mscheutz@cs.tufts.edu}{mscheutz@cs.tufts.edu}
\end{itemize}
\end{multicols} \hfill
\end{resume}
\end{document}




